Fusion Moves for Correlation Clustering

### 2014-11-10 paper/anytimefigure2.tex
inital version of text under any time plots

%!TEX root = egpaper_for_review.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[  mark size=1pt,
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]  
  \anytimeplot{image-seg}
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
   % restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    width = 1.0\columnwidth,
    scaled ticks = false,
    every axis legend/.code={\let\addlegendentry\relax} 
    ] 
    \anytimeplot{knott-3d-150}
    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/knott-3d-150.data};

@@

    \caption{knott-3d-150}

@@

  \caption{knott-3d-300}

@@

  \caption{knott-3d-450}

@@

  \caption{knott-3d-550}

@@

  \caption{seg-3d}

@@

  \caption{social nets}

@@

  \caption{normalized social nets}

@@

  \caption{modularity clustering}

@@

  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{ledgendPosition}
  \hypersetup{linkcolor = red}
  \end{center}
  \caption{
    FOO
    Among all tested solvers, the proposed method is the only
    one scaling to large 3D data.
    Except for the small 3D block, CC-Fusion finds very low
    energies one to three magnitudes faster 
    than any other method.
    With increasing block size, is outperformed even more.
    For the 2D datasets CGC is very fast, but our proposed
    solver finds lower energies while still being faster
    than the global optimal multicut solver.
  }
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%!TEX root = egpaper_for_review.tex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\pgfplotsset{every axis legend/.append style={
at={(1.0,1.2)},
anchor=north east}} 
\begin{figure*}[p]
  \begin{subfigure}[b]{0.33\textwidth}
  \centering
  \begin{tikzpicture}
  \begin{semilogxaxis}[  mark size=1pt,
  restrict y to domain=0:4620,
  xlabel = {runtime},
  xmin = 0,
  xmax = 4100,
  width = 1.0\columnwidth,
  scaled ticks = false,
  every axis legend/.code={\let\addlegendentry\relax} 
  ]  
  \anytimeplot{image-seg}
  \end{semilogxaxis}
  \end{tikzpicture}
  \caption{image-seg}\label{fig:at:image-seg}
  \end{subfigure}
  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
  \begin{subfigure}[b]{0.33\textwidth}
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
   % restrict y to domain=-6000:-4400,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    width = 1.0\columnwidth,
    scaled ticks = false,
    every axis legend/.code={\let\addlegendentry\relax} 
    ] 
    \anytimeplot{knott-3d-150}
    \addplot[color=yellow,mark=square] table[x=time,y=PIVOT*]{data3/knott-3d-150.data};

@@

    \caption{knott-3d-150}\label{fig:at:knott-150}

@@

  \caption{knott-3d-300}\label{fig:at:knott-300}

@@

  \caption{knott-3d-450}\label{fig:at:knott-450}

@@

  \caption{knott-3d-550}\label{fig:at:knott-550}

@@

  \caption{seg-3d}\label{fig:at:seg3d}

@@

  \caption{social nets}\label{fig:at:socialnets}

@@

  \caption{normalized social nets}\label{fig:at:nsocialnets}

@@

  \caption{modularity clustering}\label{fig:at:modularity}

@@

  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{ledgendPosition}
  \hypersetup{linkcolor = red}
  \end{center}
  \caption{
    % image seg
    For the image-seg instances in fig.~\ref{fig:at:image-seg} 
    Fusion-EHC-MC has performs best and Fusion-WS-MC gives 
    almost the same results, but a bit slower then with EHC proposals.
    Using the same proposals but approximate moves (Fusion-EHC-CGC Fusion-WS-CGC )
    leads to suboptimal results.
    The warm EHC started version of GCG (EHC-CGC) performs better then GCG itself,
    but both are outperformed by the proposed algorithms.
    Global optimal methods (MC-I) and the relaxed version (MC-R) are 
    still usable fast for these instances.
    % 3d 
    For the smallest 3D instances (\ref{fig:at:knott-150}) all solvers
    except ??? and EHC perform equally, and the proposed fusion algorithms
    give the best any time performance.
    With increasing problem size (\ref{fig:at:knott-150}-\ref{fig:at:knott-550} and \ref{fig:at:seg3d})
    the runtime of MC-I, MC-R and CGC increases drastically, while
    the proposed solvers still scale well.
    For these instances, the EHC started version of CGC outperforms 
    GCG in terms of runtime and energy.
    % social nets
    For the social net instances (\ref{fig:at:socialnets},\ref{fig:at:nsocialnets})
    Fusion-HC-MC and Fusion-HC-CGC perform equally.
    Only CGC and EHC-CGC leads to better energies after $10^3 sec$, while global optimal methods (MC-I)
    fail to converge within this time limit.
    % modularity clustering 
    For the modularity clustering instances in fig.~\ref{fig:at:modularity} we see
    an interesting behavior. On these complete graphs, Kernighan Lin (KL) has the 
    best performance.
    The proposed methods perform reasonable, but  KL is faster and leads to better energies.
    %%%
    %% summary
    Overall, energy hierarchical clustering based proposals work better
    then watershed based proposals. They converge to similar energies
    but the clustering based approach is faster on all tested instances.
    On all instances except for modularity clustering, it is better
    to solve the fusion move to optimality (Fusion-HC-MC) then using approximations (FUSION-HC-GCG).
  }
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-11-10 paper/egpaper_for_review.tex
inital version of text under any time plots

\section{Energy Based Hierarchical Clustering}\label{sec:ehc}

Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation
\cite{arbelaez_2006}.
In each step, the edge with the highest weight $w$ is
contracted (red edges in Fig.~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.

@@

@@

Within all experiments we used the following existing solvers 
with public available implementation.
\begin{compactitem}
    \item 
    \textbf{CGC} \cite{beier_2014_cvpr} we used the public available 
    implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}.
    As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
    Therefore we exclude those in our experiments.
    \item \textbf{KL}\cite{???}  and a public available 
        implementation 
        \footlabel{opengm-master}{%
        %\footnote{
        %    \label{opengm-master} 
            \url{https://github.com/opengm/opengm}
            %\label{opengm-master}
        }
    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified 
    version of a public available implementation implementation %\footref{opengm-master}.
    We replace a highly used queue with a more suitable and
    fast \emph{index-min-heap}\cite{???}.
    MC-R indicates that only the LP is solved, while MC-I solves
    the ILP.
    \item non vision solvers here TODO
\end{compactitem}
And the following proposed solvers:
\begin{compactitem}
\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
as described in sec.~\ref{sec:ehc}.
\item \textbf{EHC-CGC}: As CGC but warm started 
with the solution from EHC.

>>>>

\section{Energy Based Hierarchical Clustering (EHC)}\label{sec:ehc}

Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation
\cite{arbelaez_2006}.

@@

\textit{move this up} [ In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
]

@@

Within all experiments we used the following existing solvers 
with public available implementation.
\begin{compactitem}
    \item 
    \textbf{CGC} \cite{beier_2014_cvpr} we used the public available 
    implementation\footnote{\label{opengm-cvpr2014}\url{https://github.com/opengm/opengm/tree/cgc-cvpr2014}}.
    As reported in \cite{beier_2014_cvpr}, CGC is faster and gives better energies then \cite{yarkony_2012_eccv} and \cite{bagon_2011_arxiv}.
    Therefore we exclude those in our experiments.
    \item \textbf{KL}\cite{???}  and a public available 
        implementation 
        \footlabel{opengm-master}{%
        %\footnote{
        %    \label{opengm-master} 
            \url{https://github.com/opengm/opengm}
            %\label{opengm-master}
        }
    \item \textbf{MC-R,MC-I}\cite{kappes_2011_emmcvpr}  where we used a  modified 
    version of a public available implementation implementation \footref{opengm-master}.
    We replace a highly used queue with a more suitable and
    fast \emph{index-min-heap}\cite{???}.
    MC-R indicates that only the LP is solved, while MC-I solves
    the ILP.
    \item non vision solvers here TODO
\end{compactitem}
And the following proposed solvers:
\begin{compactitem}
\item \textbf{EHC}: Energy Based Based Hierarchical Clustering 
as described in sec.~\ref{sec:ehc}.
\item \textbf{EHC-CGC}: As CGC but warm started 
with the solution from EHC.
